---
title: "Introduction to femleadR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to femleadR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

`femleadR` provides tools for exploring democracy, regime, and female leadership data across 192 countries from 1950 to 2020.

## Loading the Data

```{r}
library(femleadR)

democracy_data <- load_data()
gdp_data <- load_gdp_data()
```

## Data Cleaning

`clean_democracy()` filters the GDP dataset to only rows where a female leader was recorded, removing missing values in key columns.

```{r}
female_leader_data <- clean_democracy(gdp_data)
head(female_leader_data)
```

## Plotting Regime Types Over Time

`plot_regimes()` creates a line plot comparing the count of monarchies and democracies per year.

```{r}
plot_regimes(democracy_data)
```

## Summarizing Regime Types by Year

`summarize_regimes()` returns a count of countries in each regime category per year.

```{r}
summarize_regimes(democracy_data, min_year = 2000)
```

## Top Countries by Female Leadership

`summarize_female_leaders()` returns the top countries with the most years of female national leadership and their average GDP.

```{r}
summarize_female_leaders(gdp_data, n = 10)
```

## Plotting Female Leadership

`plot_female_leaders()` creates a bar plot of the top countries by years of female national leadership.

```{r}
plot_female_leaders(gdp_data, n = 10)
```

## Statistical Analysis

`model_female_gdp()` fits a linear regression of log(GDP) on female leadership status.

```{r}
model <- model_female_gdp(gdp_data)
summary(model)
```

## Unemployment by Regime Type

`summarize_unemployment()` returns a summary table of average unemployment rates 
by regime type for a given year.

```{r}
unemp_data <- load_unemployment_data()

summarize_unemployment(unemp_data, year_filter = 2019)
```

`plot_unemployment()` creates a boxplot of unemployment rates across political 
regime types for a given year.

```{r}
plot_unemployment(unemp_data, year_filter = 2019)
```
